\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\pagenumbering{gobble}
% Spacing adjustments
\setlength{\parskip}{0.5ex}
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{1ex}{0.5ex}
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{\large\scshape}{\thesection.}{1em}{}

% Section formatting
\usepackage{xcolor}
\titleformat{\section}
  {\Large\bfseries\scshape\color{black}}
  {}
  {0em}
  {}
  [\vspace{0.2ex}\hrule]

\begin{document}

% Header with contact info
\begin{center}
    {\LARGE \textbf{Jaivir (Jay) Parmar}}\\[0.2cm]
    +1 (805) 867-5551 \,\, jay.parmar@duke.edu \,\, linkedin.com/in/Jaivir-Parmar
\end{center}

\section*{Professional Summary}
Computer science and mechanical engineering student at Duke University with hands-on experience building full-stack mobile and web applications, managing AI data pipelines, and designing scalable software systems. Proven ability to deliver end-to-end technical solutions using modern frameworks.

% Education
\section*{Education}
\textbf{Duke University}, Durham, NC \hfill Expected May 2026\\
 B.S. Computer Science, B.S.E. Mechanical Engineering, Innovation \& Entrepreneurship \hfill GPA: 3.42

% Experience
\section*{Experience}

\textbf{WisdomTree Investments — Software Engineering Intern} \hfill May 2025 -- Aug 2025\\
\textit{Frontend React Developer, New York, NY}
\begin{itemize}
    \item Designed and implemented a responsive React UI for a commission-free trading platform.
    \item Integrated real-time market data feeds to display live charts, price quotes, and portfolio metrics with socket-based updates.
    \item Collaborated with compliance and security teams to implement secure authentication flows (OAuth, multi-factor) per regulatory requirements.
    \item Optimized performance using code-splitting, lazy loading, and list virtualization for handling large portfolios and high-frequency data.

\end{itemize}

\textbf{Impression — AI-Driven Dating Profile Optimization Platform} \hfill July 2025 -- Present\\
\textit{Founder \& Lead Developer}
\begin{itemize}
    \item Architected modular TypeScript React components to enable real-time A/B testing of dating profiles.
    \item Integrated Firebase Analytics and Cloud Functions to collect and process performance metrics, supporting live feedback loops.
    \item Added GPT API for AI driven feedback based on user generated content.
    \item Built secure token economy system using Google Cloud Function calls.
    \item Created rapidly updating swipe-based UI for gamified profile rating system.
\end{itemize}

\textbf{Workly — Mobile Job Matching App} \hfill May 2025 -- July 2025\\
\textit{Founder \& Lead Developer}
\begin{itemize}
    \item Designed and deployed a full-featured SwiftUI and React Native application leveraging Firebase for real-time data syncing, authentication, Firestore database, and cloud image storage.
    \item Implemented real-time messaging using Firebase subcollections and push notifications, with dynamic UI updates and offline caching.
    \item Developed a robust admin pipeline in Python to review, edit, and categorize job postings using the Firebase Admin SDK, supporting multi-level moderation workflows.
\end{itemize}

\textbf{Duke Health — Sense to Know Study} \hfill May 2023 -- May 2025\\
\textit{Data Manager \& Frontend Developer}
\begin{itemize}
    \item Managed and validated 5,000+ infant behavioral data entries over 12 months for large scale AI-driven autism detection application.
    \item Developed a Java user interface tool to visualize and verify model training pipelines, cutting manual verification time by 40\%. Trained 10 research assistants on how to efficiently use the new UI.
\end{itemize}

% Skills
\section*{Skills}
\textbf{Languages \& Frameworks:} Java, Javascript, Python, C++, SwiftUI, HTML/CSS, Typescript, Node.js\\
\textbf{Mobile \& Web Development:} SwiftUI, Firebase, React, REST APIs, Expo, Cloud Functions\\

\end{document}
