\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}


\pagenumbering{gobble}
% Spacing adjustments
\setlength{\parskip}{0.5ex}
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{1ex}{0.5ex}
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{\large\scshape}{\thesection.}{1em}{}

% Section formatting
\usepackage{xcolor}
\titleformat{\section}
  {\Large\bfseries\scshape\color{black}} % larger, bold small caps in blue
  {} % no label
  {0em} % no separation
  {} % before-code
  [\vspace{0.2ex}\hrule] % thin rule beneath

\begin{document}

% Header with contact info
\begin{center}
    {\LARGE \textbf{Jaivir (Jay) Parmar}}\\[0.2cm]
    +1 (805) 867-5551 \,$\vert$\, jay.parmar@duke.edu \,$\vert$\, linkedin.com/in/Jaivir-Parmar
\end{center}

% Professional Summary
\section*{Professional Summary}
Duke University mechanical engineering \& computer science student with experience restoring medical devices,  designing vehicle components using CAD, managing AI data pipelines for autism detection, and developing full-stack Java/React applications; adept at delivering cross-functional technical solutions.

% Education
\section*{Education}
\textbf{Duke University}, Durham, NC \hfill Expected May 2026\\
B.S.E. Mechanical Engineering, B.S. Computer Science, Innovation \& Entrepreneurship \hfill GPA: 3.42

% Experience
\section*{Experience}

\textbf{JPcommerce} \hfill Mar 2020 -- June 2025\\
\textit{Founder \& Lead Technician}
\begin{itemize}
    \item Negotiated procurement and restoration of 100+ outdated or damaged medical equipment, generating \$100000+ revenue from online sales to private practices at a 42\% profit margin.
    \item Conducted root cause analysis and systematic troubleshooting of electromechanical systems, restoring equipment to OEM compliance and improving turnaround efficiency by 30%.
    \item Utilized precision tools and diagnostic instrumentation to refurbish devices such as autoclaves and digital radiography systems for global resale, prioritizing quality assurance and regulatory adherence.
    
\end{itemize}

\textbf{Duke Health — Sense to Know Study} \hfill May 2023 -- May 2025\\
\textit{Data Manager \& Frontend Developer}
\begin{itemize}
    \item Managed and validated 5,000+ infant behavioral data entries over 12 months for large scale AI-driven autism detection application.
    \item Developed a Java user interface tool to visualize and verify model training pipelines, cutting manual verification time by 40\%. Trained 10 research assistants on how to efficiently use the new UI.
\end{itemize}

\textbf{Full-Stack Banking Application} \hfill Sep 2024 -- Jan 2025\\
\textit{Full-Stack Developer}
\begin{itemize}
    \item Secured RESTful endpoints using Spring Security and JWT per OWASP Top 10 guidelines.
    \item Integrated Spring Boot APIs with React frontend to support account creation, transfers, and loan processing.
    \item Implemented automated email notifications for real-time transaction alerts, boosting user engagement.
\end{itemize}

\textbf{Central City Machining} \hfill May 2022 -- Aug 2022\\
\textit{CNC Operator \& Design Intern}
\begin{itemize}
    \item Programmed CNC and laser cutters to fabricate precision aftermarket engine and cosmetic components, applying lean principles to reduce setup time by 20\%.
    \item Designed SolidWorks and AutoCAD models optimized with FEA for durability and material efficiency.
    \item Utilized workshop to lead the repair of vehicles that were self-invested from private sellers. Operated on engines from manual Porsche and modern transmissions. Restored and sold for profit.
\end{itemize}

% Skills
\section*{Skills}
\textbf{Programming \& Frameworks:} Java, Python, C++, React, HTML, Website/Mobile App Development\\
\textbf{CAD \& Analysis:} SolidWorks, AutoCAD, Ansys Granta, FEA, MATLAB, Simulink,  Fusion360\\
\textbf{Fabrication \& Hardware:} CNC Machining, 3D Printing, Robotics, Mechatronics, Circuit Designing

\end{document}
