\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\pagenumbering{gobble}
% Spacing adjustments
\setlength{\parskip}{0.5ex}
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{1ex}{0.5ex}
\setlist[itemize]{noitemsep, topsep=1pt, parsep=0pt, partopsep=0pt}

% Section formatting
\titleformat{\section}{\large\scshape}{\thesection.}{1em}{}
\usepackage{xcolor}
\titleformat{\section}
  {\Large\bfseries\scshape\color{black}} {} {0em} {} [\vspace{0.2ex}\hrule]

\begin{document}

% Header with contact info
\begin{center}
    {\LARGE \textbf{Jaivir (Jay) Parmar}}\\[0.2cm]
    +1 (805) 867-5551 \,$\vert$\, jay.parmar@duke.edu \,$\vert$\, linkedin.com/in/Jaivir-Parmar
\end{center}

% Professional Summary
\section*{Professional Summary}
Dual-degree student at Duke with hands-on experience in alpha signal generation, backtesting frameworks,
execution modeling, and time-series forecasting. Passionate about market structure, derivatives, and
exploiting inefficiencies in illiquid and alternative assets.

% Education
\section*{Education}
\textbf{Duke University}, Durham, NC \hfill Expected May 2026\\
B.S.E. Mechanical Engineering, B.S. Computer Science, Innovation \& Entrepreneurship \hfill GPA: 3.5

% Experience
\section*{Experience}

\textbf{ANN-Based Derivatives Forecasting} \hfill Aug 2022 -- June 2022\\
\textit{Independent Quantitative Research}
\begin{itemize}
\item Developed alpha-generating models to forecast U.S. equity index options using historical vol data
and sentiment indicators.
\item Compared ANN-based predictions against SARIMAX and ridge regression for implied volatility sur-
face evolution.
\item Built custom backtester in Python to simulate position sizing and entry/exit triggers under liquidity
constraints.
\item Conducted slippage and signal decay analysis to evaluate real-world execution feasibility in illiquid
markets
\end{itemize}


\textbf{JPcommerce: Market Arbitrage Business} \hfill Mar 2020 -- Present\\
\textit{Founder \, \& Data-Driven Resale Strategist}
\begin{itemize}
\item Built time-dependent arbitrage models for pricing medical resale assets across fragmented secondary
marketplaces.
\item Applied techniques like mean reversion, Sharpe optimization, and private channel prediction to
maximize ROI.
\item Generated over \$100K in revenue with a 42\% margin through pricing edge and behavioral mispricing
models
\end{itemize}


\textbf{Duke Health --- Sense to Know Study} \hfill May 2023 -- Present\\
\textit{Data Manager \, \& Tooling Engineer}
\begin{itemize}
\item Designed scalable time-series ingestion pipeline across 5,000+ labeled inputs used for real-time
anomaly detection.
\item Built visual inspection tools in Java and Python for verifying statistical performance of ML-based
classification.
\item Applied statistical validation metrics (F1 score, AUC-ROC) to ensure signal reliability for live de-
ployment.
\end{itemize}

% Skills
\section*{Skills}
\textbf{Quantitative Tools:} Time-series (ARIMA/SARIMAX), ANN, volatility modeling, cointegration,
PCA, Kalman filters, signal decay, statistical arbitrage, slippage modeling\\
\textbf{Programming:} Python (pandas, NumPy, scikit-learn, statsmodels, PyTorch), C++, Java, Bash,
SQL\\
\textbf{Backtesting/Infra} Zipline, custom backtesters, REST APIs, execution modeling, event simulations\\
\textbf{Finance:} Derivatives chains, price arbitrage, futures, prediction markets

\end{document}
